### 2018-04-10 latex/icpp18/experiments.tex
synthetic dataset

\subsection{Experimental Setup}

\subsubsection{Datasets}\label{sec:datasets}

We use two datasets from Flickr.com and Delicious.com that involves images tagged with different labels by users.
The rows of the matrix correspond to different images, whereas the columns of the matrix represent different tags. The value of each nonzero $a_{i,j} \in \Am$ indicates the number of unique users that tagged the image $i$ with the tag $j$.
Flickr and Delicious matrices are of size 28Mx1.6M and 17Mx2.5M, and have 112M and 72M nonzero elements, respectively.
The current implementation of \mpifaun can only operate when $R$ and $C$ can divide $m$ and $n$, hence we trimmed the matrices slightly.

>>>>

\subsection{Experimental Setup}
In this paper, we use both synthetic and realworld datasets. The synthetic datasets are used to evaluate the communication
 strategies with the increase in number of non-zeros of the sparse matrices. 
\subsubsection{Datasets}\label{sec:datasets}

{\em Synthetic:} For synthetic sparse matrices, we used the popular Kronecker generator from Graph500 benchmark (\url{http://www.graph500.org/}). The graph generator is a Kronecker generator similar to the Recursive MATrix (R-MAT) scale-free graph generation algorithm \cite{CZF04}. This model recursively sub-divides the adjacency matrix of the graph into four equal-sized partitions and distributes edges within these partitions with unequal probabilities. Initially, the adjacency matrix is empty, and edges are added one at a time. The parameters to the generator are the number of vertices $N$ and the Edge Factor ($ef$) that defines the ratio of the graph?s edge count to its vertex count (i.e., half the average degree of a vertex in the graph). Typically, the number of edges $M$ of the scale free graph will be $ef \times N$. In our case, we consider $2^{20}$($\approx$ 1.05 million) vertices and set of edge factor $ef$=\{4,8,16,32,64\}.

{\em Real World:} We use two datasets from Flickr.com and Delicious.com that involves images tagged with different labels by users.
The rows of the matrix correspond to different images, whereas the columns of the matrix represent different tags. The value of 
each nonzero $a_{i,j} \in \Am$ indicates the number of unique users that tagged the image $i$ with the tag $j$.
Flickr and Delicious matrices are of size 28Mx1.6M and 17Mx2.5M, and have 112M and 72M nonzero elements, respectively.
The current implementation of \mpifaun can only operate when $R$ and $C$ can divide $m$ and $n$, hence we trimmed the matrices slightly.
